Guarded Recursion in Agda via Sized Types

### 2019-04-22 code-oneclock-paper/latex/Introduction.tex
Grammar fixes

Utilizing techniques for representing ``type theory in type theory''
\cite{AltenkirchK16,Chapman09}, we present an Agda formalization of
the syntax of a simple type theory for guarded recursion. This object
language, which we call \GTT, is a variant of Atkey and McBride's type
system for productive coprogramming \cite{atkey2013productive} in
which the clock context can contain at most one clock. The types of
\GTT\ include the aforementioned \IC{▻} modality and a \IC{□} modality,
a nameless analogue of Atkey and McBride's universal clock
quantification. Clouston \etal \ \cite{CloustonBGB15} studied a
guarded variant of lambda calculus extended with a \IC{□} operation,
which they call ``constant''.  Our object calculus differs from
theirs in that our judgments are indexed by a clock context, which can
be empty or containing exactly one clock. 
%In this respect \GTT\ is closer in spirit to Atkey and McBride's
%language.
The design of \GTT\ has the benefit of allowing a more appealing introduction rule for
\IC{□} than Clouston et al.'s.

>>>>

Utilizing techniques for representing ``type theory in type theory''
\cite{AltenkirchK16,Chapman09}, we present an Agda formalization of
the syntax of a simple type theory for guarded recursion. This object
language, which we call \GTT, is a variant of Atkey and McBride's type
system for productive coprogramming \cite{atkey2013productive} in
which the clock context can contain at most one clock. The types of
\GTT\ include the aforementioned \IC{▻} modality and a \IC{□} modality,
a nameless analogue of Atkey and McBride's universal clock
quantification. Clouston \etal \ \cite{CloustonBGB15} studied a
guarded variant of lambda calculus extended with a \IC{□} operation,
which they call ``constant''.  Our object calculus differs from
theirs in that our judgments are indexed by a clock context, which can
be empty or containing exactly one clock. 
%In this respect \GTT\ is closer in spirit to Atkey and McBride's
%language.
The design of \GTT\ has the benefit of allowing a more appealing introduction rule for
\IC{□} than Clouston \etal 's.
\GTT\ also differs from Clouston \etal 's calculus in the class of definable
guarded recursive types. We follow Atkey and McBride's approach and
restrict the least fixpoint operator \IC{μ} to act on strictly positive
functors, while \IC{μ} type former in Clouston \etal solely operates on functors
in which all variables are guarded by an occurrence of the \IC{▻} modality.

### 2019-04-22 code-oneclock-paper/latex/paper.tex
started appendix
Work on appendix, added product
Grammar fixes

%%%%%%%%%%%%%   AMS MATH  %%%%%%%%%%%%%%
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{mathtools}

@@

\input{Presheaves/Const}
\input{Presheaves/Exp}

@@

\section{Conclusions and Future Work}
\label{sec:concl}
We presented a simple type theory for guarded recursion that we called \GTT. We
formalized its syntax and semantics in Agda. Sized types
were employed to interpret the characteristic
features of guarded recursion. From this, we conclude that guarded
recursion can be simulated using sized types. We greatly benefited
from the fact that sized types constitute a native feature of Agda, so
we were able to fully develop our theory inside a proof assistent.

@@

>>>>

%%%%%%%%%%%%%   AMS MATH  %%%%%%%%%%%%%%
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{proof}
\usepackage{stmaryrd}

@@

\input{Presheaves/Product}
The weakening type former \IC{↑} of \GTT\ is modeled using the constant presheaf, which we denote by \AF{Const}.
\input{Presheaves/Exp}

@@

\section{Conclusions and Future Work}
\label{sec:concl}
We presented a simple type theory for guarded recursion that we called \GTT. We
formalized its syntax and semantics in Agda. Sized types
were employed to interpret the characteristic
features of guarded recursion. From this, we conclude that guarded
recursion can be simulated using sized types. We greatly benefited
from the fact that sized types constitute a native feature of Agda, so
we were able to fully develop our theory inside a proof assistant.

@@

\input{Appendix}
